Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
Commenting Background section

\textbf{Function space}
%As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
%Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
%be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
%In most applications, we care about predictions from the neural network and not the weights themselves.
%As such, it is the distribution over function values that we are actually interested in.
While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves. Consequently, the weight-space posterior corresponds to a distribution over function values. Imagine sampling from the weight posterior; the resulting functions could be viewed as perturbations of the function at the MAP estimate $f_{\vw^*}$. This perspective aligns better with the main objective in most applications: making representative predictions given the observations we have.

@@

% Discussion points
It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
so the function space prior (and thus posterior) is only a locally linear approximation.
In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.

>>>>

\textbf{Function space} \todo{Could be titled some other way, like Function-space representation}
%As a neural network is a deterministic mapping, the weight-space posterior induces a distribution over the function values.
%Intuitively, if one was to sample from the weight posterior, the corresponding functions created can
%be viewed as perturbed versions of the function at the MAP estimate $f_{\vw^*}$.
%In most applications, we care about predictions from the neural network and not the weights themselves.
%As such, it is the distribution over function values that we are actually interested in.
While neural networks are deterministic mappings defined by their weights, the ultimate goal of training a neural network is to optimize the function it represents, not the weights themselves. Consequently, the weight-space posterior corresponds to a distribution over function values. Imagine sampling from the weight posterior; the resulting functions could be viewed as perturbations of the function at the MAP estimate $f_{\vw^*}$. This perspective aligns better with the main objective in most applications: making representative predictions given the observations we have.

@@

% Discussion points
It is worth noting that the NTK linearises the network around the MAP solution $\weights^{*}$,
so the function-space prior (and thus posterior) is only a locally linear approximation.
In contrast to conventional GP kernels, the NTK does not have any hyperparameters which need to be learned.
It is also worth noting that the NTK may be highly non stationary and is dependent on the NN architecture, for example, the activation functions.
